\textit{Monami} as an oscillatory hydrodynamic instability in a submerged sea grass bed

### 2014-10-06 Paper/grass.tex
added figure with single colorbar and modified tex file accordingly

% We use a mean field model for the coupling between the flow and the vegetation. 
The drag exerted by the vegetation on the flow is approximated by a continuous body force $\mathbf{f}=-N_g\mathbf{f_d}$,  where $\mathbf{f_{d}}$ is the drag force per unit length of the grass blade, and $N_g$ the grass blade number density per unit horizontal area \cite{Vivoni98,Nepf99,Ghisal02,Delangre04,Delangre06}. 
This drag enters the governing equations of continuity and momentum balance, written as 
\begin{equation}
\quad \grad\cdot\bu = 0,\hspace{3mm} \rho \left(\bu_{t}+\bu.\grad\bu \right) = -\grad p+\mu\grad^{2}\bu +\mathbf{f}+\rho\mathbf{g}
\label{navier-stokes}
\end{equation}
where $\rho$ is the fluid density, $\mathbf{u}$ the velocity, 
$p$ the pressure, $\mu$ the eddy viscosity (the flow is turbulent) and $\mathbf{g}$ the acceleration due to gravity. 
The Reynolds number of the flow based on the scale of the grass blade is $O(10^2-10^3)$; therefore the form drag on the vegetation dominates over the skin-friction. 
We model it as 
$\mathbf{f_{d}}=C_N \rho u_{N}^{2}d\bn$, 
where $d$ is the average width of grass blade projected in the flow direction, $C_{N}$ the drag coefficient, and $u_{N}$ and $\bn$ are the velocity component and unit vector normal to the grass (see fig.~\ref{basicflow} for a schematic). 
In the field, both $C_N$ and $N_g$ vary with position, but we do not expect these variations to be central to the instability mechanism, and therefore take $C_N$ and $N_g$ to be constants. 
Based on previous experiments \cite{Vivoni98}, we take $C_N \approx 1$.
\newline
\begin{figure*}
\begin{tabular}{cccc}
{\includegraphics[height = 4cm, width = 5.8cm]{Set4_dens28_imgsc}} &
%{\includegraphics[scale = 0.67]{Set4_dens30_imgsc}} &
{\includegraphics[height = 4cm,width = 5.8cm]{Set4_dens32_imgsc}} &
{\includegraphics[height = 4.15cm,width=6.5cm]{Set4_dens34_imgsc}} \\
{\includegraphics[height = 4cm, width = 5.8cm]{Set5_dens38_imgsc}} &
%{\includegraphics[scale = 0.67]{Set5_dens40_imgsc}} &
{\includegraphics[height = 4cm, width = 5.8cm]{Set5_dens42_imgsc}} &
{\includegraphics[height = 4.15cm,width=6.5cm]{Set5_dens46_imgsc}} \\

@@

\end{tabular}

>>>>

% We use a mean field model for the coupling between the flow and the vegetation. 
The drag exerted by the vegetation on the flow is approximated by a continuous body force $\mathbf{f}=-N_g\mathbf{f_d}$,  where $\mathbf{f_{d}}$ is the drag force per unit length of the grass blade, and $N_g$ the grass blade number density per unit horizontal area \cite{Vivoni98,Nepf99,Ghisal02,Delangre04,Delangre06}. 
This drag enters the governing equations of continuity and momentum balance, written as 
\begin{equation}
\quad \grad\cdot\bu = 0,\hspace{3mm} \rho \left(\bu_{t}+\bu.\grad\bu \right) = -\grad p+\mu\grad^{2}\bu +\mathbf{f}+\rho\mathbf{g}
\label{navier-stokes}
\end{equation}
where $\rho$ is the fluid density, $\mathbf{u}$ the velocity, 
$p$ the pressure, $\mu$ the eddy viscosity (the flow is turbulent) and $\mathbf{g}$ the acceleration due to gravity. 
The Reynolds number of the flow based on the scale of the grass blade is $O(10^2-10^3)$; therefore the form drag on the vegetation dominates over the skin-friction. 
We model it as 
$\mathbf{f_{d}}=C_N \rho u_{N}^{2}d\bn$, 
where $d$ is the average width of grass blade projected in the flow direction, $C_{N}$ the drag coefficient, and $u_{N}$ and $\bn$ are the velocity component and unit vector normal to the grass (see fig.~\ref{basicflow} for a schematic). 
In the field, both $C_N$ and $N_g$ vary with position, but we do not expect these variations to be central to the instability mechanism, and therefore take $C_N$ and $N_g$ to be constants. 
Based on previous experiments \cite{Vivoni98}, we take $C_N \approx 1$.
\newline
\begin{figure*}
 \includegraphics{SetAll_imgsc}
%\end{figure}
%\begin{figure*}
%\begin{tabular}{cccc}
%{\includegraphics[height = 4cm, width = 5.8cm]{Set4_dens28_imgsc}} &
%{\includegraphics[scale = 0.67]{Set4_dens30_imgsc}} &
%{\includegraphics[height = 4cm,width = 5.8cm]{Set4_dens32_imgsc}} &
%{\includegraphics[height = 4.15cm,width=6.5cm]{Set4_dens34_imgsc}} \\
%{\includegraphics[height = 4cm, width = 5.8cm]{Set5_dens38_imgsc}} &
%{\includegraphics[scale = 0.67]{Set5_dens40_imgsc}} &
%{\includegraphics[height = 4cm, width = 5.8cm]{Set5_dens42_imgsc}} &
%{\includegraphics[height = 4.15cm,width=6.5cm]{Set5_dens46_imgsc}} \\

@@

%\end{tabular}
